---
title: "Consider Altitude as the Primary Source of Error"
output:
  html_document:
    df_print: paged
---
```{r}
source("/Users/anacristinaeguigurenburneo/Documents/DJI_Mini2_Measurement_Error/Scripts/Gal23_DroneMeasurementError.R")
```

If most of the error comes from altitude miscalculations, what should the altitude be given our known parameters:

Fixed:
alpha: 1.2646
boat length:12.03

Variable:
pixel length
image width


First, invert equation so a "true.altitude" can be estimated given the known values. 

```{r}
true.altitude <- function(true.length, pixel.length, image.width, alpha){
  true.altitude = (true.length/pixel.length) * (image.width/alpha)
}
```

Next, calculate the true.altitude
```{r}
dat$true.altitude <- true.altitude(true.length = 12.03, 
                                   pixel.length = dat$pixel.length, 
                                   image.width = dat$ImageWidth, 
                                   alpha = 1.2646)
```

Now, estimate the altitude errors:
```{r}
dat$altitude.error <- dat$true.altitude-dat$altitude.fix
hist(dat$altitude.error, xlab = "altitude error", main = "", breaks = 100)
text(x = 20, y = 40, paste("mean error = ", signif(mean(dat$altitude.error, digits =2))))
```

Simulate the error in length estimates if we added this correction factor to the reported altitude
```{r}
dat$altitude.corr <- dat$altitude.fix+mean(dat$altitude.error)
dat$length.corr <- morpho.length.alpha(altitude = dat$altitude.corr,
                                      image.width = dat$ImageWidth,
                                      length.pixels = dat$pixel.length)


```
average = 12.20

vs just adding the mean length error
```{r}
mean(dat$length.fix.a - mean(dat$length.error))
```

